\huge A Usability Evaluation of Tor Launcher

### 2016-11-04 pets2017-paper/pets2017-paper.tex
rewrote conclusion section

{\color {blue}
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface. A couple sentences to summarize the whole thing. Echo roadmap in intro, but make it summary-like.

%proof that user testing is important and general advice to for more research on Tor
Tor doesn't collect any information or perform AB testing, so this type of user research is especially important. to set it up, get users, computers, consent, and instrumented versions of the software. Research can be exploratory (ask users what they want), observational (look at what they do), or testing a hypothesis (verify changes). We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software. Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.

%Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
}

>>>>

%proof that user testing is important and general advice to for more research on Tor
Tor Browser version~4.5 incorporated textual and navigational changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>. The authors have discussed  alternative ways to bootstrap a connection to Tor without requiring users to configure network components with Tor developers, and they were open to considering some of our ideas for future improvements.

We encourage more researchers to perform this type of usability testing for other parts of Tor Browser and other Tor applications, especially because it provides user insight to company that does not collect user data. You can help by performing usability research that uncovers unknown problems, tests out new ideas, or verifies the impact of recently made changes. We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software. Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
